### 2019-08-05 reports/thesis/chapters/4_variancePrediction.tex
Update varmean
Grouped shading corrections together in GlmSelect and VarMeanCv
Residual analysis
Write variancePrediction chapter

Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120}. The procedure was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data. The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.

@@

\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\

@@

\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}     

@@

\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilterDeg120}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 100 repeats.}
\label{table:meanVar_glmselect_absnofilter}

@@

\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\

@@

\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}     

@@

\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilterDeg120}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 100 repeats.}
\label{table:meanVar_glmselect_absfilter}

@@

The results are shown in Tables \ref{table:meanVar_glmselect_absnofilter} and \ref{table:meanVar_glmselect_absfilter}. The models selected all have only two terms and are quite simple. Different shading correction or different criteria had no effect on the selected model. The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 100 repeats consistently selected the same model.

There was some variation to the selected models between datasets. For example when using the identity link, \texttt{AbsNoFilterDeg120} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilterDeg120} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$. Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}+\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$. Figures \ref{fig:meanVar_varMeanExample_AbsNoFilterDeg120} and \ref{fig:meanVar_varMeanExample_AbsFilterDeg120} shows the GLM fits. There is a leverage towards the low grey values because there are more low grey values in the dataset. As a result, the GLM does not capture the curvature towards the high grey values.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilterDeg120} with linear shading correction. The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsNoFilterDeg120}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilterDeg120} with linear shading correction. The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsFilterDeg120}
\end{figure}

>>>>

Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter}. The procedure was repeated 10 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data. The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.

@@

\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identitycriterion.txt} \\

@@

\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalcriterion.txt}     

@@

\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{30}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 10 repeats.}
\label{table:meanVar_glmselect_absnofilterdeg30}

@@

\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identitycriterion.txt} \\

@@

\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalcriterion.txt}     

@@

\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{120}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 10 repeats.}
\label{table:meanVar_glmselect_absnofilterdeg120}

@@

\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identitycriterion.txt} \\
\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalcriterion.txt}     
\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 10 repeats.}
\label{table:meanVar_glmselect_absfilterdeg30}
\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identitycriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identityorder.txt}     \\
                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identityvote.txt}      \\
                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identitycriterion.txt} \\
\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalcriterion.txt} \\ \hline
\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalorder.txt}     \\
                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalvote.txt}      \\
                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalcriterion.txt}     
\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}. The columns of the table represent different shading corrections used on the projections. Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data. The row labelled order shows the most common selected polynomial orders. The error bars are the standard deviation from the 10 repeats.}
\label{table:meanVar_glmselect_absfilterdeg120}

The results are shown in Tables \ref{table:meanVar_glmselect_absnofilterdeg30} and \ref{table:meanVar_glmselect_absnofilterdeg120} for \texttt{AbsNoFilter} and Tables \ref{table:meanVar_glmselect_absfilterdeg30} and \ref{table:meanVar_glmselect_absfilterdeg120} for for \texttt{AbsFilter}. The models selected all have only two terms and are quite simple. Different shading correction or different criteria had no effect on the selected model. The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 10 repeats consistently selected the same model.

There was some variation to the selected models between datasets. For example when using the identity link, \texttt{AbsNoFilter} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilter} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$. Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}+\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.

Figures \ref{fig:meanVar_varMeanExample_AbsNoFilter} and \ref{fig:meanVar_varMeanExample_AbsFilter} shows the GLM fits for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively. The prediction intervals were obtained using the distribution $\widehat{Y}(x)\sim\gammaDist\left(\alpha, \dfrac{\alpha}{g^{-1}\left(\widehat{\eta}(x)\right)}\right)$ where $\widehat{\eta}(x)$ is the fitted systematic component. The fits all looked reasonable except for \texttt{AbsNoFilter} at \ang{120} where the fit did not capture the inflection. The forward stepwise selection may not pick this up because there are a lot of low grey values, causing a leverage towards these low grey values and the inflection does not stand out to the method.
